Titeln på avhandlingens språk

### 2022-09-07 model.tex
discussing

Both scenarios described above use a variant of one of the \num{169}-step tasks used in~\cite{olguinmunoz:impact2021}, truncated to \num{45} steps.
\medskip

@@

\cref{fig:scaling_duration} illustrates the results for scenario \labelcref{verification:scaling}. 
It showcases the important behaviors of the realistic models which are not captured by naive, non-adaptive model.
On one hand, the realistic models (and by extension, humans) are actually faster than the naive model by up to \SI{4.37}{\percent} at the lowest level of impairment.
This is due to the speed-up effect described in \textcite{olguinmunoz:impact2021} --- humans get faster as a task progresses with a high system responsiveness.

On the other, the realistic models experience a slowdown of about \SI{5.13}{\percent} at the highest levels of impairment when compared to the naive model.
This is explained by the reduced system responsiveness either negating the speed-up effect, or directly leading to the \emph{additional} behavioral slowdown previously described~\cite{olguinmunoz:impact2021}.
It should be noted that for the \numlist{7;10} client setups only about \SI{6}{\percent} and \SI{22}{\percent} of \acp{TTF} fell into the medium impairment level, and practically no \acp{TTF}

>>>>

Both scenarios described above use a variant of one of the \num{169}-step tasks used in~\cite{olguinmunoz:impact2021}, truncated to \num{45} steps.

\medskip

@@

\cref{fig:scaling_duration} illustrates the results for scenario \labelcref{verification:scaling}. 
It showcases the important behaviors of the realistic models which are not captured by the naive, non-adaptive model.
On one hand, the realistic models (and by extension, humans) are actually faster than the naive model by up to \SI{4.37}{\percent} in a deployment with no resource contention.
This is due to the speed-up effect described in \textcite{olguinmunoz:impact2021} --- humans get faster as a task progresses with a high system responsiveness.

On the other, the realistic models experience a mean slowdown of about \SI{5.13}{\percent} at the highest level of resource contention (\num{10} concurrent loops) when compared to the naive model, even though only about \SI{22}{\percent} of \acp{TTF} in this scenario reach the medium impairment level and practically no \acp{TTF} pass threshold for the highest level of impairment.
This showcases that the additional user slow-down due to reduced system responsiveness described in \textcite{olguinmunoz:impact2021} causes a noticeable and significant  even at lower and medium levels of impairment.
\todo[inline]{Add another setup with additional load and discuss}

\medskip

We illustrate the results of scenario \labelcref{verification:neuro} in \cref{fig:neuro_duration}.
